\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-25 OaklandSubmission/eval.tex
finishing pass on 6

%dataset | time | comm | timeL | timeW | comm
\subsection{Deep neural nets}
\label{sec:dnneval}
We evaluate \tool on the DNNs described in \minion~\cite{minionn} and
report the results in Table~\ref{tab:nn}\footnote{\minion does
  not report the network round-trip time.}.
Our goal here is to demonstrate that \tool
can provide performance competitive to specialized protocols for DNNs
described in~\cite{secureml,cryptonets,minionn}.  
The first benchmark  is the DNN described in SecureML~\cite{secureml}.
It has three fully connected layers with square as the activation function.
This DNN is light-weight as it requires only arithmetic computations
(additions and multiplications) 
except for the {\it argmax} at the end.
Next, we implement the DNN described in Cryptonets~\cite{cryptonets} in \tool.
This DNN also uses square as the activation function and has one
convolution (with 5 output channels) and one fully connected layer. 
Finally, we compare against \minion on a CNN
with two convolutions (with 16 output channels each) and two fully
connected layers. 
In contrast to the previous two DNNs, this DNN uses ReLU for activation and
has significantly higher number of boolean-and gates.
Recall, that square activation can be implemented entirely using
arithmetic gates but ReLU requires boolean-and gates.  For a complete
description of these benchmarks and their accuracies,  the reader is
referred to the original references.

For the benchmarks in Table~\ref{tab:nn}, \minion
outperforms SecureML and Cryptonets and columns 2 and 3 show the time taken by \minion. 
The column ``Model size'' is the number of 32 bit integers in the trained model.
We observe that our performance is competitive with \minion in the LAN
and the WAN settings and the lines of code required are still small. 
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient
preprocessing phase and has SIMD 
(single instruction multiple data) capabilities that allow \minion to perform
matrix operations efficiently. Our language and compiler 
focus on generic 2PC and such optimizations are beyond the scope of this paper.
However, \minion also reports performance results on a bigger DNN with
7 convolution layers. 
This benchmark requires pipelining and we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length

@@

We next present \bonsai~\cite{bonsai} results on three
standard datasets: character recognition (Chars4k~\cite{campos},
accuracy 74.71\%), text recognition (USPS~\cite{hull}, accuracy
94.4\%), and object categorization (WARD~\cite{yang}, accuracy
95.7\%). 
The \bonsai models are already over integers and no porting from
floating-point is required.
We implement the trained classifiers in \tool for all the benchmarks
from~\cite{bonsai},
and show the represenative results in Table~\ref{tab:bonsai}.
Out of all the benchmarks from~\cite{bonsai}, the dataset WARD
requires the largest model. 
The column ``depth''  shows the depth of the
tree used by \bonsai. The size of \tool 
program grows with the depth of the tree, as the straightforward \tool
implementation requires a loop for each layer of the
tree. \aseem{Should we remark here that once we have functions in the
  language, LOC would come down, perhaps in the footnote?}

@@

\subsection{Partitioning}
\label{sec:pipeeval}
The largest benchmark of \minion~\cite{minionn} is a DNN for CIFAR-10
dataset~\cite{cifar}. 
The classifier's task is to categorize colored ($32\times 32$) images
into 10 classes. A secure evaluation of this DNN needs more memory
than what is available
on our machines \aseem{Is there limitation machine RAM or ABY
  limit?}. Therefore, we use partitioning and divide the
computation into seven stages. 
The first step does a convolution with 64 output channels and a ReLU
activation. The next four stages together perform a convolution that
involves multiplying a $64\times 576$ matrix with a 
$576\times 1024$ matrix. The sixth stage performs a ReLU and a
convolution. The final stage has four convolutions, five ReLUs, and a
fully connected layer. The total number of lines of \tool code for
this benchamrk is 336 lines. \aseem{Would it be better if we had
  functions, for loop expressions etc.? If so, we should add a
  footnote.}

>>>>

%dataset | time | comm | timeL | timeW | comm
\subsection{Deep neural nets}
\label{sec:dnneval}
We evaluate \tool on the DNNs described in SecureML~\cite{secureml},
Cryptonets~\cite{cryptonets}, and CNN from \minion~\cite{minionn}. For
comparison, we consider their implementations from
\minion~\cite{minionn}, which outperforms their previous
implementations. Table~\ref{tab:nn} shows the
results\footnote{\minion does not report the network round-trip time.}.
We note that for each of these DNNs, \minion provides a
specialized protocol, while \tool uses a generic 2PC protocol
(auto) generated from high-level code.

The first benchmark  is the DNN described in
SecureML~\cite{secureml}.
It has three fully connected layers with square as the activation function.
This DNN is light-weight as it requires only arithmetic computations
(additions and multiplications) 
except for the $\mathsf{argmax}$ at the end.
Next, we implement the DNN described in Cryptonets~\cite{cryptonets}
in \tool.
This DNN also uses square as the activation function and has one
convolution (with 5 output channels) and one fully connected layer. 
Finally, we implement CNN from \minion, that has
two convolutions (with 16 output channels each) and two fully
connected layers.  In contrast to the previous two DNNs, it uses
ReLU for activation and
has significantly higher number of boolean-and gates.
Recall, that square activation can be implemented entirely using
arithmetic gates but ReLU requires boolean-and gates.  For a complete
description of these benchmarks and their accuracies, we refer the
reader to the original references.

In Table~\ref{tab:nn}, columns 2 and 3 show the time taken by \minion.
The column ``Model size'' is the number of 32 bit integers in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient
preprocessing phase and has SIMD 
(single instruction multiple data) capabilities that allow it to perform
matrix operations efficiently. In contrast, \tool focuses on generic
2PC, and such optimizations are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length

@@

We next present \bonsai~\cite{bonsai} results on three
standard datasets: character recognition (Chars4k~\cite{campos},
accuracy 74.71\%), text recognition (USPS~\cite{hull}, accuracy
94.4\%), and object categorization (WARD~\cite{yang}, accuracy
95.7\%). 
The \bonsai models are already over integers and no porting from
floating-point is required.
We implement the trained classifiers in \tool for all the benchmarks
from~\cite{bonsai},
and show the represenative results in Table~\ref{tab:bonsai}.
Out of all the benchmarks from~\cite{bonsai}, the dataset WARD
requires the largest model. 
The column ``depth''  shows the depth of the
tree used by \bonsai. The size of \tool 
program grows with the depth of the tree, as the straightforward \tool
implementation requires a loop for each layer of the
tree. \aseem{Should we remark here that once we have functions in the
  language, LOC would come down, perhaps in the footnote? Else a PL
  reviewer might scoff at it :).}

@@

\subsection{Partitioning}
\label{sec:pipeeval}
The largest benchmark of \minion~\cite{minionn} is a DNN for CIFAR-10
dataset~\cite{cifar}. 
The classifier's task is to categorize colored ($32\times 32$) images
into 10 classes. A secure evaluation of this DNN needs more memory
than what is available
on our machines \aseem{Is the limitation machine RAM or ABY
  limit?}. Therefore, we use partitioning and divide the
computation into seven stages. 
The first step does a convolution with 64 output channels and a ReLU
activation. The next four stages together perform a convolution that
involves multiplying a $64\times 576$ matrix with a 
$576\times 1024$ matrix. The sixth stage performs a ReLU and a
convolution. The final stage has four convolutions, five ReLUs, and a
fully connected layer. The total number of lines of \tool code for
this benchamrk is 336 lines. \aseem{Would it be better if we had
  functions, for loop expressions etc.? If so, we should add a
  footnote.}
